Split codes into chunks

### 2015-09-22 011-split-codes.Rmd
Testing split codes

```{r}
ny_1850_pattern <- regex("(\n§((\\s+)?)\\d+((\\.)?)|\n\\$((\\s+)?)\\d+((\\.)?)|\nchapter|\ntitle|\narticle|\nt i t l e|\nRULE \\w+\\.|\n\\d{4,}\\.|\nSEC((\\.)?)\\s+\\d+((\\.)?)|\n8EC((\\.)?)\\s+\\d+((\\.)?)|\nSE0((\\.)?)\\s+\\d+((\\.)?)|\nSEO((\\.)?)\\s+\\d+((\\.)?)|\nSEQ((\\.)?)\\s+\\d+((\\.)?))", ignore_case = TRUE)
test <- str_detect(c("\n§ 1842 This should be true", "\nThis should be false §",
                     "\n§ 142. This should be true", "\nThis should be false §",
                     "\n§142. This should be true", "\nThis should be false §",
                     "\nchapter should be true", "\nThis chapter should be false",
                     "\nCHAPTER should be true", "\nthis CHAPTER should be false",
                     "\nT I T L E should be true", "false",
                     "\n$342. This should be true", "false",
                     "\n$ 323. This should be true", "false",
                     "\nRULE XVI. This should be true", "This rule is false",
                     "\n3652. From AL1852 true", "232. False",
                     "\n3652. From AL1852 true", "Citation 232. False",
                     "\nSEC. 431. true", "This SEC 133 false",
                     "\n8EC. 3323. true", "false",
                     "\nSEC.   2545 true", "false"),
                   pattern = ny_1850_pattern)
all(test == c(TRUE, FALSE))
```

@@

```{r}
split_doc("legal-codes/NY1850.txt", ny_1850_pattern, "legal-codes-split/NY1850")
split_doc("legal-codes/CA1851.txt", ny_1850_pattern, "legal-codes-split/CA1851")
split_doc("legal-codes/NC1868.txt", ny_1850_pattern, "legal-codes-split/NC1868")
split_doc("legal-codes/AL1852.txt", ny_1850_pattern, "legal-codes-split/AL1852")
split_doc("legal-codes/OH1853.txt", ny_1850_pattern, "legal-codes-split/OH1853")
split_doc("legal-codes/OH1853extended.txt", ny_1850_pattern, "legal-codes-split/OH1853extended")
split_doc("legal-codes/CA1850.txt", ny_1850_pattern, "legal-codes-split/CA1850")
split_doc("legal-codes/GA1860.txt", ny_1850_pattern, "legal-codes-split/GA1860")
split_doc("legal-codes/CA1868.txt", ny_1850_pattern, "legal-codes-split/CA1868")
split_doc("legal-codes/AZ1865.txt", ny_1850_pattern, "legal-codes-split/AZ1865")
```

>>>>

```{r}
ny_1850_pattern <- regex("(\n§((\\s+)?)\\d+((\\.)?)|\n\\$((\\s+)?)\\d+((\\.)?)|\nchapter|\ntitle|\narticle|\nSUBDIVISION|\nt i t l e|\nRULE \\w+\\.|\n\\d{4,}\\.|\nSEC((\\.)?)\\s+\\d+((\\.)?)|\nSECTION((\\.)?)\\s+\\d+((\\.)?)|\nSECT((\\.)?)\\s+\\d+((\\.)?)|\n8EC((\\.)?)\\s+\\d+((\\.)?)|\nSE0((\\.)?)\\s+\\d+((\\.)?)|\nSEO((\\.)?)\\s+\\d+((\\.)?)|\nS((\\.)?)\\s+\\d+((\\.)?)|\nSEQ((\\.)?)\\s+\\d+((\\.)?)|\nArt((\\.)?)\\s+\\d+((\\.)?)|\nAn((\\.)?)\\s+\\d+((\\.)?)|\nAm((\\.)?)\\s+\\d+((\\.)?))", ignore_case = TRUE)
test <- str_detect(c("\n§ 1842 This should be true", "\nThis should be false §",
                     "\n§ 142. This should be true", "\nThis should be false §",
                     "\n§142. This should be true", "\nThis should be false §",
                     "\nchapter should be true", "\nThis chapter should be false",
                     "\nCHAPTER should be true", "\nthis CHAPTER should be false",
                     "\nT I T L E should be true", "false",
                     "\n$342. This should be true", "false",
                     "\n$ 323. This should be true", "false",
                     "\nRULE XVI. This should be true", "This rule is false",
                     "\n3652. From AL1852 true", "232. False",
                     "\n3652. From AL1852 true", "Citation 232. False",
                     "\nSEC. 431. true", "This SEC 133 false",
                     "\n8EC. 3323. true", "false",
                     "\nSEC.   2545 true", "false",
                     "\nSECTION 143. true", "false"),
                   pattern = ny_1850_pattern)
all(test == c(TRUE, FALSE))
```

@@

```{r}
split_doc("legal-codes/NY1850.txt", ny_1850_pattern, "legal-codes-split/NY1850")
split_doc("legal-codes/CA1851.txt", ny_1850_pattern, "legal-codes-split/CA1851")
split_doc("legal-codes/NC1868.txt", ny_1850_pattern, "legal-codes-split/NC1868")
split_doc("legal-codes/AL1852.txt", ny_1850_pattern, "legal-codes-split/AL1852")
split_doc("legal-codes/OH1853.txt", ny_1850_pattern, "legal-codes-split/OH1853")
split_doc("legal-codes/OH1853extended.txt", ny_1850_pattern, "legal-codes-split/OH1853extended")
split_doc("legal-codes/CA1850.txt", ny_1850_pattern, "legal-codes-split/CA1850")
split_doc("legal-codes/GA1860.txt", ny_1850_pattern, "legal-codes-split/GA1860")
split_doc("legal-codes/CA1868.txt", ny_1850_pattern, "legal-codes-split/CA1868")
split_doc("legal-codes/AZ1865.txt", ny_1850_pattern, "legal-codes-split/AZ1865")
split_doc("legal-codes/DT1887.txt", ny_1850_pattern, "legal-codes-split/DT1887")
split_doc("legal-codes/LA1825.txt", ny_1850_pattern, "legal-codes-split/LA1825")
split_doc("legal-codes/MA1858.txt", ny_1850_pattern, "legal-codes-split/MA1858")
split_doc("legal-codes/AR1868.txt", ny_1850_pattern, "legal-codes-split/AR1868")
```
